%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Developer} % Job title
    {Kapsch TrafficCom} % Organization
    {Jönköping, Sweden} % Location
    {Jan. 2019 - ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Vehicle classification}
        \item {Object detection of vehicle axles}
        \item {Robot camera calibration: UI development and calibration implementation}
        \item {Team responsibility for sprint planning}
        \item {\textbf{Tools:} Python, C++, Keras, Docker, Git, Jira}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Developer} % Job title
    {Veoneer} % Organization
    {Linköping, Sweden} % Location
    {Aug. 2018 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Pedestrian and vehicle classification for autonomous vehicles}
        \item {Visualization tool for machine learning algorithms' performance}
        \item {\textbf{Tools:} C++, Python, Keras, Git, Gerrit}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master's Thesis Student} % Job title
    {Veoneer} % Organization
    {Linköping, Sweden} % Location
    {Jan. 2018 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Active Learning for Road Segmentation using Convolutional Neural Networks}
        \item {Investigated how model uncertainty can limit training data by letting the model select it's own data}
        \item {\href{https://liu.diva-portal.org/smash/get/diva2:1259079/FULLTEXT01.pdf}{Published at liu.diva-portal.org}}
        \item {\textbf{Tools:} Keras, Python, LaTeX, Matplotlib}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Softare Developer - Summer Internship} % Job title
    {Autoliv} % Organization
    {Linköping, Sweden} % Location
    {Jun. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Visualization tool for machine learning algorithm's performance}
        \item {Evaluation and visualization of DGPS calibration system}
        \item {\textbf{Tools:} C++, Python}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer - Summer Internship and Part Time} % Job title
    {Teknomedia} % Organization
    {Norrköping, Sweden} % Location
    {Jun. 2016 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data mining and visualization of customer databases}
        \item {Web application for filtering and visualization of customer data}
        \item {\textbf{Tools:} SQL, C\#, JavaScript, HTML}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
